Metropolitan Areas (Deaths & Case)

### 2020-11-11 KPMG Team/Dashboard/msa_areas.Rmd
state county map viz
MSA Latest
with link to socialexplorer variables

# census data API, variables can be changed here 
census <- get_acs(geography = "county",
                   variables = c(population = "B01003_001E"), # total population), # black veterans 
                   output = "wide",
                   county = "",
                   year = 2018)

@@

>>>>

# census data API, variables can be changed here 
# find variable names: https://www.socialexplorer.com/data/ACS2010/metadata/?ds=ACS10
census <- get_acs(geography = "county",
                   variables = c(population = "B01003_001E"), # total population), # black veterans 
                   output = "wide",
                   county = "",
                   year = 2018)

@@

# Plot State Map with Metro Areas

# mapping packages needed 
library(leaflet)
library(maptools)
library(rgdal)

library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
